Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-23 ApproximateCode.tex
version 4.6

To address this challenge, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems. The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
\end{abstract}

@@

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}
\vspace{-3mm}
\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}
\vspace{-3mm}
\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}\vspace{-3mm}
\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

@@

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced.
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

Use cases for approximate storage range from transient memory to embedded settings and mass storage cloud servers. Mapping approximate data onto blocks that have exhausted their hardware error correction resources, for example, to extend memory endurance. On embedded settings, it enables the reduction of the cost of accesses and preserve battery life to loosen the capacity constraints. \cite{sampson2014approximate} Here, in data-center-scale video database, approximate storage can provide multiple levels of fault tolerance for data of different importance, avoiding redundant backup for the less-important data, thus saving a significant amount of space.

Approximate storage loosens the requirement of storage reliability by allowing quality loss of some specific data. Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks. The critical data is still safe because they are stored and sufficiently backed up by expensive and highly reliable storage devices. Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.

%However, it is too naive to store data in approximate storage units indiscriminately. Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution. To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs. Therefore, it is very important to distinguish the importance of video data.

\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{1.2cm}<{\centering}|p{2.1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|}
\hline
Layer & Schemes & Storage Overhead & Fault Tolerance & Computing Overhead \\ \hline
\begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} & Data Compression & low & / & high \\ \hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}} & RS-based EC for 3DFTs & high & high & high \\ \cline{2-5} 
 & XOR-based EC for 3DFTs & high & high & low \\ \cline{2-5} 
 & RAID-6 & low & low & low \\ \cline{2-5} 
 & RAID-5 & medium & medium & low \\ \cline{2-5} 
 & Approximate Storage & very low & very low & low \\ \cline{2-5} 
 & Approximate Code & low & high & low \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

\subsubsection{Decoding Time under One Failure Node Condition Analysis}
The results are shown in Figure \ref{fig-decoding-1}.
\begin{itemize}
    \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code. The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
    \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node. The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-1-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-1-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-1-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-1-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
    \end{figure}

\subsubsection{Decoding Time under Two Failure Nodes Condition Analysis}
The results are shown in Figure \ref{fig-decoding-2}.
\begin{itemize}
    \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition. The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
    \item LRC Codes:
    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes. The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-2-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-2-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-2-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-2-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
    \end{figure}

\subsubsection{Decoding Time under Three Failure Nodes Condition Analysis}
The results are shown in Figure \ref{fig-decoding-3}.
\begin{itemize}
    \item STAR Code: the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition. The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
    \item LRC Codes:
    We could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes. The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-3-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-3-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-3-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-3-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
    \end{figure}

\begin{figure*}[!ht]
    \subfigure{
        \label{fig-encoding-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Encoding.eps}
    }
    \subfigure{
        \label{fig-decoding-1-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-1.eps}
    }
    \subfigure{
        \label{fig-decoding-2-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-2.eps}
    }
    \subfigure{
        \label{fig-decoding-3-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-3.eps}
    }
    \caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
    \end{figure*}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-recovery-2}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
    }
    \subfigure{
        \label{fig-recovery-3}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
    }
    \vspace{-0.3cm}
    \caption{Recovery time comparison in two and three disk between Approximate Code and other ECs}\label{fig-recovery}
    \end{figure}

>>>>

To address this challenge, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems. The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 1.25X when double disks fail.
\end{abstract}

@@

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[height=6cm]{photo/STAR.pdf}\label{fig-star}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=6cm]{photo/TIP.pdf}\label{fig-tip}
}\vspace{-3mm}
\caption{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

@@

\subsection{Approximate Storage}
Approximate storage is an innovative approach for storage devices \cite{zhao2017approximate, sampson2014approximate, guo2016high, jevdjic2017approximate}, which enable applications to store data approximately. It can improve the performance, lifetime, or reduce the power consumption of different storage devices.

Specifically, for video applications, there are several approximate storage methods \cite{guo2016high, jevdjic2017approximate} for bit-level reliability in progressively encoded multimedia data.  \cite{guo2016high} identifies the relative importance of the encoded bits on the image quality and apply different levels of error correction. \cite{jevdjic2017approximate} shows how reliability of video storage can be traded for density and achieves the optimal quality/density points by tracking visual and metadata dependencies within the encoded bit stream.

\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
\hline
Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
RAID-6 & low & low & low & \\ \cline{1-4} 
RAID-5 & medium & medium & low & \\ \cline{1-4} 
Approximate Storage & very low & very low & low & \\ \cline{1-4} 
Approximate Code & low & high & low & \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
LRC($k,l,r$) & $1+(l+r)/k$ & $r+1$ & $r+2$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

\subsubsection{Decoding Time under Single Node Failure Condition Analysis}
The results are shown in Figure \ref{fig-decoding-1}.
\begin{itemize}
    \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code. The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
    \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node. The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-1-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-1-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-1-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-1-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}
    \end{figure}

\subsubsection{Decoding Time under Double Node Failure Condition Analysis}
The results are shown in Figure \ref{fig-decoding-2}.
\begin{itemize}
    \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition. The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
    \item LRC Codes:
    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes. The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-2-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-2-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-2-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-2-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-2-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in Double Node Failure between Approximate Code and other method}\label{fig-decoding-2}
    \end{figure}

\subsubsection{Decoding Time under Triple Node Failure Condition Analysis}
The results are shown in Figure \ref{fig-decoding-3}.
\begin{itemize}
    \item STAR Code: the rate of optimization is up to $83.5\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    \item TIP Code: This condition is similar to STAR code. The rate of optimization is up to 82.2\% (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 5$).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under three failure nodes condition. The rate of optimization is up to $96.7\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
    \item LRC Codes:
    We could see that Approximate Code largely reduces the decoding time when three nodes fail, compared with LRC codes. The rate of optimization is up to $98.3\%$  (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-3-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-3-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-3-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-3-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-3-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Decoding Time Comparison in Triple Node Failure between Approximate Code and other method}\label{fig-decoding-3}
    \end{figure}

\begin{figure*}[!ht]
    \subfigure{
        \label{fig-encoding-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Encoding.eps}
    }
    \subfigure{
        \label{fig-decoding-1-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-1.eps}
    }
    \subfigure{
        \label{fig-decoding-2-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-2.eps}
    }
    \subfigure{
        \label{fig-decoding-3-combine}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Bar-Decoding-3.eps}
    }
    \caption{Comparison of several matrics between different methods when the number of data nodes is 5}\label{fig-BAR}
    \end{figure*}

@@

\begin{figure}[ht]
    \subfigure{
        \label{fig-recovery-2}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-2.eps}
    }
    \subfigure{
        \label{fig-recovery-3}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Recovery-3.eps}
    }
    \vspace{-0.3cm}
    \caption{Recovery time comparison in double and triple node failures between Approximate Code and other ECs}\label{fig-recovery}
    \end{figure}
